A Minimal Demo of \texttt{glyphmaps}

### 2012-06-03 paper/demo.Rnw
wrote new grid() function that works like glyph() to turn a layer into a gridded layer.

<<glyphmaps-fig-8>>=
p <- ggplot(seasons) + 
  map_us +
  glyph(
    geom_line(aes(x = time, y = pred)), 
    major = aes(lon[1], lat[1]), glyph.by = "stn", 
    ref = ref_box(aes(fill = avg)))
@

>>>>

<<glyphmaps-fig-8>>=
p <- ggplot(seasons) + 
  map_us +
  glyph(
    geom_line(aes(x = time, y = pred)), 
    major = aes(I(grid(lon)),I(grid(lat))), glyph.by = grid_by(lon, lat))
, 
    ref = ref_box(aes(fill = avg)))
@
